A Data-Driven Framework for Neural Field Modeling

### 2011-01-05 ltx/first_order_framework/LaTeX_Manuscript.tex
added a comment on Lopez Da Silva and Zetterberg citation

For models to be clinically viable, they must be patient-specific. A possible approach to achieve this would be to fit a general continuum neural field model, like the \citet{Wilson1973} (WC) or \citet{Amari1977} models, or a neural mass model like the \citet{Jansen1995} model, to patient-specific data. Fitting the neural models to individuals is a highly non-trivial task. Recently, however, this task has been approached from a number of standpoints. \dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} using an extended Kalman filter. This paper demonstrated for the first time the feasibility of assimilating data with neural models of EEG.}

>>>>

For models to be clinically viable, they must be patient-specific. A possible approach to achieve this would be to fit a general continuum neural field model, like the \citet{Wilson1973} (WC) or \citet{Amari1977} models, or a neural mass model like the \citet{Jansen1995} model, to patient-specific data. Fitting the neural models to individuals is a highly non-trivial task. Recently, however, this task has been approached from a number of standpoints. \dean{(Reviewer 1, additional comment d):) The first paper on patient specific modeling came from~\citet{Valdes1999}, where they fit a neural mass model of \citet{LopesDaSilva1976} and \citet{Zetterberg1978} \parham{using an extended Kalman filter--need to check (it's not extended Kalman filter I think)}. This paper demonstrated for the first time the feasibility of assimilating data with neural models of EEG.}
